### 2014-10-31 fundamentals/acros.tex
added neams
adds CI
misspelled some acros

\newacronym{MIT}{MIT}{the Massachusettes Institute of Technology}

@@

\newacronym{GDSE}{GDSE}{Generic Disposal Sytem Environment}
\newacronym{GPAM}{GPAM}{Generic Performance Asessment Model}

@@

\newacronym{OCRWM}{OCRWM}{Office of Civillian Radioactive Waste Management}

@@

\newacronym{HPC}{HPC}{High-Performace Computing}

@@

\newacronym{VV}{V\&V}{Verificaion and Validation}

@@

>>>>

\newacronym{MIT}{MIT}{the Massachusetts Institute of Technology}

@@

\newacronym{GDSE}{GDSE}{Generic Disposal System Environment}
\newacronym{GPAM}{GPAM}{Generic Performance Assessment Model}

@@

\newacronym{OCRWM}{OCRWM}{Office of Civilian Radioactive Waste Management}

@@

\newacronym{HPC}{HPC}{High-Performance Computing}

@@

\newacronym{VV}{V\&V}{Verification and Validation}

@@

\newacronym{NEAMS}{NEAMS}{Nuclear Engineering Advanced Modeling and Simulation}
\newacronym{CI}{CI}{Continuous Integration}
